---
title: "Week 4 developing data product"
author: "Marco Lamers"
date: "16-8-2020"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library( shiny )
```

## Shiny Presentation
- Have my doubts on the exact tasks that are asked for week 4 assignments.
I created a server.R and UI.R that displayed three different types of interactions in one page.
Not so very Nice but Ok. 
- Now I am embedding that code in an R markdown. Again not so very nice.
- Then they are asking about providing proper documentation.
Are we expected to create it like a package?
For now I expect not to.
- I learned a lot with practicing these steps whatsoever
- now asking for RStudio Connect usage; again my doubts. I will use RPubs for the app.

## Old Faithful separated; template based

```{r eruptions}
inputPanel(
            h3( "Show HTML understanding"),
            sliderInput("bins",
                        "Number of bins:",
                        min = 1,
                        max = 50,
                        value = 30
                        )
  )
#adding the ({ after renderplot makes the special marker visible })
renderPlot({
        x    <- faithful[, 2]
        bins <- seq(min(x), max(x), length.out = input$bins + 1)

        # draw the histogram with the specified number of bins
        hist(x, breaks = bins, col = 'darkgreen', border = 'white' )
})
```

## Random points example
Some more experiments for controlling the layout.
In fact amazingly simple.


```{r try 2}
    sidebarLayout(
        sidebarPanel(
            h4( "- Points thing"),
            numericInput( "numeric", "how many numbers to be plotted?", 
                          value = 100, min=1, max=500, step = 1 ),
            sliderInput( "sliderX", "pick minium and maximum X values", 
                         -100, 100, value = c(-50,50)),
            sliderInput( "sliderY", "pick minium and maximum Y values", 
                         -100, 100, value = c(-50,50)),
        ),

        # Show a plot of the generated distribution 
        mainPanel(
            h4( "Second: some random points"),
renderPlot({
        set.seed( 2020-08-16)
        number_of_points <- input$numeric
        minX <- input$sliderX[1]
        maxX <- input$sliderX[2]
        minY <- input$sliderY[1]
        maxY <- input$sliderY[2]
        
        dataX <- runif( number_of_points, minX, maxX)
        dataY <- runif( number_of_points, minY, maxY)
        
        title = "week 4 part 1"
        renderText( number_of_points )
        
        plot( dataX, dataY, xlab = "X axis", ylab = "Y axis", main = title,
              xlim=c(-100,100),ylim=c(-100,100))
    })
        )
    )

    
```

## R Output; just an output table for Shiny

```{r Iris}
  renderTable({iris })
```


